---
title: "AIDs Drug"
author: "Christina Jilavdaryan"
date: "10/2/21"
output: html_document
---

```{r include=FALSE,echo=FALSE}
require(tidyverse)
require(tigerstats)
triUmp <-read.csv(file="triUmpsal.csv",header=TRUE)
```

# Introduction

<!--In this section you explain what you are trying to show.  Where did the data come from?  What is the research or other question you are trying to answer?.  If you skimp in this section expect to be marked down in your grade. Paint a picture of the project a couple of paragraphs is expected!-->

A new  preventative aides drug (triUmpsal) is under test in clinical trials. Consider only the females, does this drug seem effective?  Hint - use dplyr to obtain that subpopulation with the filter command.

$H_0$: Among women there is no difference in terms of percent of those who contracted aids and got the vaccine and those that didn't get the vaccine 


$H_A$: Among women there is a difference between the percent of those who contracted aids and got the vaccine and those that didn't get the vaccine 


# Methods

<!--Decide on your methods:  use "variable analysis" or other appropriate descriptors.  Make sure to choose at least one graphical method and at least one numerical method. Discuss what data manipulations may be needed for example subsetting or other binning procedures and what sort of graphical displays and inferential tools will be used!-->

For this project we will use categorical~categorical because the data used is organized in categories. With the response variable being did people get infected, and the explanatory variable being if they got the vaccine with results limited to the female population.

# Results

<!--Divide this section into two sub-sections:  One for your descriptive  results and one for your inferential results.!-->

```{r}
WomanData=filter(triUmp,gender=="F")
head(WomanData)
```


These are the data for the women in the study showing who got the drug vs who got the placebo.

## Descriptive Results

### Graphical Descriptive Results


```{r}
barchartGC(~infected + treatment,data=WomanData)
barchartGC(~infected + treatment,data=WomanData, type="percent")

```

#### Plot barplots ggplot way

```{r}
dd2 <- WomanData%>% group_by(infected,treatment) %>% summarize(count=n()) %>% mutate(prcnt=count/sum(count))


# the group_by followed by summarize(count=n())

basicC <- ggplot(dd2,aes(x=infected,y=count,fill=treatment))
basicC + geom_bar(stat="identity",position="dodge")

#Now for percentage plot

basicCC <- ggplot(dd2,aes(x=infected,y=prcnt*100,fill=treatment)) 
basicCC + geom_bar(stat="identity", position = "dodge")
```

<!--Graphical results here.  Make sure to show your code.  Provide appropriate labels for axes, giving units if possible, and provide a good title for the graph, too.  Use the graphical results to describe the patterns if any that exist in the data as focused toward the research question. Bottom line is to explain the features of the graph that are relevant to conforming or departing to what is expected by your null hypothesis !-->

This box plot shows that out of the women who got aids, most of them had taken the vaccine before contracting aids. So the women who took the experimental vaccine were more likely to contract aids than those who got the placebo. 

### Numerical Descriptive Results

<!--Numerical results go here. Use the numerical results to describe the patterns if any that exist in the data as focused toward the research question!-->

```{r}
table1 <- xtabs(~infected + treatment, data=WomanData)
rowPerc(table1)
colPerc(table1)
```

This table shows that 59% of the women who contracted aids had gotten the vaccine beforehand and 41% did not get the vaccine.

## Inferential Results

<!--State hypothesis clearly.  Make sure your discussion of the inferential test covers all the aspects that the test output produces, such as test statistic, p-value etc.  Make a decision about the null hypothesis, explain the assumptions on which the selected test/procedure was based, and why the chosen procedure satisfys the assumptions and is appropriate to answer the research question!-->


```{r}
chisq.test(table1)
chisqtestGC(table1)
fisher.test(table1)
```

Out of the three tests ran, all showed p-values that were too low so the chances of recreating the same results are unlikely, so we reject the null hypothesis because there was a significant difference between the infection rates of those who got the vaccine and those who got the placebo.


# Discussion and Conclusion

<!--Discussion and conclusion here.  If you found a relationship be sure to consider whether the relationship occurs because one of the variavbles causes the other, or whether they perhasps are related for some other reason.  Watch the chapter 6 videos from the GeorgeTown videos collection.!-->


The results showed us that the odds ratio of contracting the aids virus after getting the vaccine is 1.543902:1, the reason this is significant is that the confidence ratio shows that it is over 1 (1.240408, 1.925729) so there is a 95% chance that women who take the vaccine are more likely to acquire aids than women who got the placebo making the vaccine is ineffective against aids inflection protection. We reject the null hypothesis because the charts establish that the vaccine do not work against preventing women from contracting aids, and increases the chances of contracting the virus in women so there is a significant difference between those who get the vaccine and those who get the placebo.
